graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-05-09 paper/paper.Rmd
correct figure subcaptions

#plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
          scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)))
mtext(text = "(b) relationship matrix", side=1, line=3.5, at=0, adj=0.5, cex=1.75)

@@

```{r, include=FALSE}
pdf("Plotsimulation_activating-5.pdf", width = 13.44, height = 6.72)
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "", mar = c(6, 6), keysize = 1)
mtext(text = "samples", side=1, line=1.5, at=0.55, adj=0.5, cex=1.5)
mtext(text = "genes", side=4, line=1, at=0.45, adj=0.5, cex=1.5)
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3.5, at=0.5, adj=0.5, cex=1.75)
dev.off()
system("sed -i.bak '/Plotsimulation_activating-5/s/\\\\(.*\\\\)width=[.]415/\1width=.830/g' paper.md && rm paper.md.bak")
system("sed -i.bak '/Plotsimulation_activating-5/s/\\\\(.*\\\\)width=[.]415/\1width=.830/g' paper.tex && rm paper.tex.bak")
```

@@

```{r, include=FALSE}
pdf("Plotsimulation_inhibiting-5.pdf", width = 13.44, height = 6.72)
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "", mar = c(6, 6), keysize = 1)
mtext(text = "samples", side=1, line=1.5, at=0.55, adj=0.5, cex=1.5)
mtext(text = "genes", side=4, line=1, at=0.45, adj=0.5, cex=1.5)
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3.5, at=0.5, adj=0.5, cex=1.75)
dev.off()
system("sed -i.bak '/Plotsimulation_inhibiting-5/s/\\\\(.*\\\\)width=[.]415/\1width=.830/g' paper.md && rm paper.md.bak")
system("sed -i.bak '/Plotsimulation_inhibiting-5/s/\\\\(.*\\\\)width=[.]415/\1width=.830/g' paper.tex && rm paper.tex.bak")
```

@@

plot_directed(graph, state = state, layout = layout.kamada.kawai,
              border.node=scales::alpha("black", 0.75), fill.node="lightblue",
              col.arrow = c(scales::alpha("navyblue", 0.25), scales::alpha("red", 0.25))[state], 
              cex.node = 1.5, cex.label = 0.8, cex.arrow = 2, 
              sub = expression(paste("(a) TFG-", Beta, " activates SMADs")), cex.sub = 1.75)
box()

@@

# #plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
          scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "")
mtext(text = "(b) relationship matrix", side=1, line=3.5, at=0, adj=0.5, cex=1.75)

@@

```{r, include=FALSE}
pdf("Plotsimulation_smad-5.pdf", width = 13.44, height = 6.72)
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "", mar = c(6, 6), keysize = 1)
mtext(text = "samples", side=1, line=1.5, at=0.55, adj=0.5, cex=1.5)
mtext(text = "genes", side=4, line=1, at=0.45, adj=0.5, cex=1.5)
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3.5, at=0.5, adj=0.5, cex=1.75)
dev.off()
system("sed -i.bak '/Plotsimulation_smad-5/s/\\\\(.*\\\\)width=[.]415/\1width=.830/g' paper.md && rm paper.md.bak")
system("sed -i.bak '/Plotsimulation_smad-5/s/\\\\(.*\\\\)width=[.]415/\1width=.830/g' paper.tex && rm paper.tex.bak")
```

>>>>

#plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
          scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)))
mtext(text = "(b) Relationship matrix", side=1, line=3.5, at=0, adj=0.5, cex=1.75)

@@

```{r, include=FALSE}
pdf("Plotsimulation_activating-5.pdf", width = 13.44, height = 6.72)
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "", mar = c(6, 6), keysize = 1)
mtext(text = "samples", side=1, line=1.5, at=0.55, adj=0.5, cex=1.5)
mtext(text = "genes", side=4, line=1, at=0.45, adj=0.5, cex=1.5)
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3.5, at=0.5, adj=0.5, cex=1.75)
dev.off()
#system("sed -i.bak '/Plotsimulation_activating-5/s/\\(.*\\)width=[.]415/\1width=.830/g' paper.md && rm paper.md.bak")
#system("sed -i.bak '/Plotsimulation_activating-5/s/\\(.*\\)width=[.]415/\1width=.830/g' paper.tex && rm paper.tex.bak")
#sed -i '/Plot.*-5/s/\(.*\)width=[.]415/\1width=.830/g' paper.md paper.tex
```

@@

```{r, include=FALSE}
pdf("Plotsimulation_inhibiting-5.pdf", width = 13.44, height = 6.72)
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "", mar = c(6, 6), keysize = 1)
mtext(text = "samples", side=1, line=1.5, at=0.55, adj=0.5, cex=1.5)
mtext(text = "genes", side=4, line=1, at=0.45, adj=0.5, cex=1.5)
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3.5, at=0.5, adj=0.5, cex=1.75)
dev.off()
#("sed -i.bak '/Plotsimulation_inhibiting-5/s/\\(.*\\)width=[.]415/\1width=.830/g' paper.md && rm paper.md.bak")
#system("sed -i.bak '/Plotsimulation_inhibiting-5/s/\\(.*\\)width=[.]415/\1width=.830/g' paper.tex && rm paper.tex.bak")
#sed -i '/Plot.*-5/s/\(.*\)width=[.]415/\1width=.830/g' paper.md paper.tex
```

@@

plot_directed(graph, state = state, layout = layout.kamada.kawai,
              border.node=scales::alpha("black", 0.75), fill.node="lightblue",
              col.arrow = c(scales::alpha("navyblue", 0.25), scales::alpha("red", 0.25))[state], 
              cex.node = 1.5, cex.label = 0.8, cex.arrow = 2, 
              sub = expression(paste("(a) TFG-", beta, " activates SMADs")), cex.sub = 1.75)
box()

@@

# #plot relationship matrix
heatmap.2(make_distance_graph(graph, absolute = FALSE),
          scale = "none", trace = "none", col = colorpanel(50, "white", "red"),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "")
mtext(text = "(b) Relationship matrix", side=1, line=3.5, at=0, adj=0.5, cex=1.75)

@@

```{r, include=FALSE}
pdf("Plotsimulation_smad-5.pdf", width = 13.44, height = 6.72)
#plot simulated expression data
heatmap.2(expr, scale = "none", trace = "none", col = bluered(50),
colsep = 1:length(V(graph)), rowsep = 1:length(V(graph)), labCol = "", mar = c(6, 6), keysize = 1)
mtext(text = "samples", side=1, line=1.5, at=0.55, adj=0.5, cex=1.5)
mtext(text = "genes", side=4, line=1, at=0.45, adj=0.5, cex=1.5)
mtext(text = "(e) Simulated expression data (log scale)", side=1, line=3.5, at=0.5, adj=0.5, cex=1.75)
dev.off()
#system("sed -i.bak '/Plotsimulation_smad-5/s/\\(.*\\)width=[.]415/\1width=.830/g' paper.md && rm paper.md.bak")
#system("sed -i.bak '/Plotsimulation_smad-5/s/\\(.*\\)width=[.]415/\1width=.830/g' paper.tex && rm paper.tex.bak")
#sed -i '/Plot.*-5/s/\(.*\)width=[.]415/\1width=.830/g' paper.md paper.tex
```

### 2020-05-09 paper/paper.tex
correct figure subcaptions

\CommentTok{#plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

@@

\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state =}\NormalTok{ state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{border.node=}\NormalTok{scales}\OperatorTok{::}\KeywordTok{alpha}\NormalTok{(}\StringTok{"black"}\NormalTok{, }\FloatTok{0.75}\NormalTok{), }\DataTypeTok{fill.node=}\StringTok{"lightblue"}\NormalTok{,}
              \DataTypeTok{col.arrow =} \KeywordTok{c}\NormalTok{(scales}\OperatorTok{::}\KeywordTok{alpha}\NormalTok{(}\StringTok{"navyblue"}\NormalTok{, }\FloatTok{0.25}\NormalTok{), scales}\OperatorTok{::}\KeywordTok{alpha}\NormalTok{(}\StringTok{"red"}\NormalTok{, }\FloatTok{0.25}\NormalTok{))[state], }
              \DataTypeTok{cex.node =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{cex.label =} \FloatTok{0.8}\NormalTok{, }\DataTypeTok{cex.arrow =} \DecValTok{2}\NormalTok{, }
              \DataTypeTok{sub =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"(a) TFG-"}\NormalTok{, Beta, }\StringTok{" activates SMADs"}\NormalTok{)), }\DataTypeTok{cex.sub =} \FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\CommentTok{# #plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{labCol =} \StringTok{""}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

>>>>

\CommentTok{#plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)))}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) Relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}

@@

\KeywordTok{plot_directed}\NormalTok{(graph, }\DataTypeTok{state =}\NormalTok{ state, }\DataTypeTok{layout =}\NormalTok{ layout.kamada.kawai,}
              \DataTypeTok{border.node=}\NormalTok{scales}\OperatorTok{::}\KeywordTok{alpha}\NormalTok{(}\StringTok{"black"}\NormalTok{, }\FloatTok{0.75}\NormalTok{), }\DataTypeTok{fill.node=}\StringTok{"lightblue"}\NormalTok{,}
              \DataTypeTok{col.arrow =} \KeywordTok{c}\NormalTok{(scales}\OperatorTok{::}\KeywordTok{alpha}\NormalTok{(}\StringTok{"navyblue"}\NormalTok{, }\FloatTok{0.25}\NormalTok{), scales}\OperatorTok{::}\KeywordTok{alpha}\NormalTok{(}\StringTok{"red"}\NormalTok{, }\FloatTok{0.25}\NormalTok{))[state], }
              \DataTypeTok{cex.node =} \FloatTok{1.5}\NormalTok{, }\DataTypeTok{cex.label =} \FloatTok{0.8}\NormalTok{, }\DataTypeTok{cex.arrow =} \DecValTok{2}\NormalTok{, }
              \DataTypeTok{sub =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"(a) TFG-"}\NormalTok{, beta, }\StringTok{" activates SMADs"}\NormalTok{)), }\DataTypeTok{cex.sub =} \FloatTok{1.75}\NormalTok{)}
\KeywordTok{box}\NormalTok{()}

@@

\CommentTok{# #plot relationship matrix}
\KeywordTok{heatmap.2}\NormalTok{(}\KeywordTok{make_distance_graph}\NormalTok{(graph, }\DataTypeTok{absolute =} \OtherTok{FALSE}\NormalTok{),}
          \DataTypeTok{scale =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{trace =} \StringTok{"none"}\NormalTok{, }\DataTypeTok{col =} \KeywordTok{colorpanel}\NormalTok{(}\DecValTok{50}\NormalTok{, }\StringTok{"white"}\NormalTok{, }\StringTok{"red"}\NormalTok{),}
\DataTypeTok{colsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{rowsep =} \DecValTok{1}\OperatorTok{:}\KeywordTok{length}\NormalTok{(}\KeywordTok{V}\NormalTok{(graph)), }\DataTypeTok{labCol =} \StringTok{""}\NormalTok{)}
\KeywordTok{mtext}\NormalTok{(}\DataTypeTok{text =} \StringTok{"(b) Relationship matrix"}\NormalTok{, }\DataTypeTok{side=}\DecValTok{1}\NormalTok{, }\DataTypeTok{line=}\FloatTok{3.5}\NormalTok{, }\DataTypeTok{at=}\DecValTok{0}\NormalTok{, }\DataTypeTok{adj=}\FloatTok{0.5}\NormalTok{, }\DataTypeTok{cex=}\FloatTok{1.75}\NormalTok{)}
